\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=.75in,top=.75in,right=.75in,bottom=.75in]{geometry} % Document margins
% \newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
% \newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \usepackage[document]{ragged2e}
\usepackage[none]{hyphenat}
\usepackage{hyperref}

\name{Eric A. Stephens} 
\address{10 Echodale Ave \\ Baldwinsville, NY 13027 \\ 315.406.4100 \\ e.a.stephens@me.com} 

\begin{document}
\begin{rSection}{Profile}
I help enterprises evolve their business and technical capabilities and provide justification for doing so. Excelled in roles across strategy consulting, sales engineering, enterprise architecture, and software engineering. Fluent in numerous technological domains in a variety of industries including retail, life sciences, mobile telecom, media \&entertainment, financial services, healthcare, and public sector.

\end{rSection}

\begin{rSection}{Experience}

\textbf{VP, Enterprise Architecture \& Strategy / Chief of Staff} \hfill Sep 2021 - present\\
Fidelity - Fidelity Architecture \& Engineering - Corporate Technology Group \hfill \textit{Merrimack, NH}\\
Engaged in multi-faceted role within FAE-CTG leading Enterprise Document Management (EDM) capabilities, orchestrating strategy \& planning / Chief of Staff duties for the Chief Architect, pioneering domain-level business architecture and portfolio management practices, and improving enterprise architecture (EA) practices through an EA Guild.

\begin{itemize}
   \itemsep -3pt {} 
   \item \textbf{S\&P Lead / Chief of Staff}. Led virtual S\&P team coordinating numerous planning activities across the practice including planning cycles, KPI definition, and domain-level work allocation. Spearheaded the (re-) adoption of Agile practices to gain improved transparency into work activity for Chief Architect. 
   \item \textbf{Business Architecture}. Leveraged extensive EA experience to further evolve architects knowledge and use of business architecture thinking. Refactored and aligned capabilities and solutions in effort to rationalize and streamline the portfolio. Advocated for leading business architecture practices within team and to broader TAG-BP community leading talks and sharing perspectives. Mentored lead architects in various aspects of their roles as enterprise architects.
   \item \textbf{EA Guild}. Led continuous improvement activities with virtual team \~25 of solution architects across the CTG practice to improve architects' skills, define repeatable processes and reusable artifacts for consistent, value-driven delivery.
   \item \textbf{EDM}. Provided leadership of team evolving this capability including creation of common APIs, contingent architectures, and Accessibility solutions to support critical enterprise capability. 
 \end{itemize}

Simultaneously, represented the FAE-CTG team with the EA governance body (TAG-BP), co-lead the AI Ethics workgroup with publication of a quarterly newsletter, provided consultative services for the Log4Shell vulnerability (ca. 2021) response and APS architecture refactoring (Autumn 2022), and led / contributed to several Common Impact projects providing advisory services to non-profits. 
 
\textbf{Principal, Business Value Consulting - Americas} \hfill Oct 2016 - Sep 2021\\
Commvault \hfill \textit{Tinton Falls, NJ}\\
Achieved or exceeded revenue targets in dual role elevating our collaboration in accounts resulting in expanded deal size. Engaged broader into channel ecosystem to establish new partners. Develop and deliver enablement material to assist in pre-sales requirements engineering / discovery practices.

Led role in developing next iteration of GTM process for EA-centric, capability-driven advisory engagements. Leveraged strategic consulting and EA practices in a highly tailored fashion. Formulated market sizing analysis for strategic partners to drive pipeline.

While maintaining business activities demonstrated personal leadership capabilities:
\begin{itemize}
  \itemsep -3pt {} 
  \item Led Communities of Interest efforts around cloud computing to identify pertinent trends to Data Management
  \item Achieved two cloud certifications within a 3 month period
  \item Recipient of Wingman Award Q4FY2018 and Above \& Beyond FY2018Q1 for excellence in deal execution and thought leadership
  \item Developed virtual lab utilizing IaC for testing software-defined storage platform. See \url{https://github.com/Commvault/hedvig-lab}
\end{itemize}

\textbf{Engagement Manager} \hfill Apr 2015 - Oct 2016\\
Strategy\&, part of the PwC network \hfill \textit{New York, NY}\\
Participated and led strategy engagements for healthcare clients focusing on business capability evolution and organization / culture change:
\begin{itemize}
  \itemsep -3pt {} 
  \item Developed offering strategy for growing IT services firm to expand services and markets
  \item Executed rapid process improvement assessment to address encounter submission challenges for government payor BPO. Synthesized assessment framework along with short and long-term recommendations.
  \item Developed strategy to advance software testing practices addressing process and operating model optimization leading to notable cost savings.  
  \item Led team to develop eWorking capability strategy addressing mounting real estate costs, decreasing employee satisfaction, and difficult talent attraction.
  \item Refined capability model and assessed maturity as part of investment prioritization effort for mid-sized insurer. Contributed to engagement team mobilization, deliverables, and IP.
\end{itemize}
While executing projects, developed thought leadership on next generation Enterprise / Capabilities Architecture, Electronic Collaboration Suites, and IoT for Health Care Payers. Provided leadership support for internal EA community of practice, supported business development efforts, and mentored new staff.

\textbf{Oracle Enterprise Architect / Enterprise Architecture Director} \hfill Jun 2010 - Apr 2015\\
Oracle Corporation \hfill \textit{Redwood Shores, CA}\\
Demonstrated executive-level engagement in formulating actionable EA roadmaps for clients in several vertical domains. Specialized in business architecture, application rationalization/transformation, public sector health care programs, and EA governance. Key accomplishments include:
\begin{itemize}
  \itemsep -3pt {} 
  \item Construction and management of full EA traceability model to support Health Insurance Exchange program with emphasis on business architecture.
  \item Authored identity management blueprint to improve employee on-boarding for a retailer.
  \item Re-chartered EA programs to drive investment value realization in public sector health care, retail, and mortgage banking.
  \item Screened candidates and mentor staff within EA role and served on the business architecture certification board.
  \item Recognized as OEA of the Year FY2013 and FY2011Q3
\end{itemize}
Simultaneously with client engagements, contributed to internal collateral on Information Architecture and EA Governance. Engaged in business development activities and interacted with global EA community and industry forums including speaking engagements. Ongoing interviews and contributions to Oracle Magazine.

\end{rSection} 

\textbf{Senior Director, Enterprise Architecture / Enterprise Architect} \hfill May 2021 - Jun 2010\\
Excellus BlueCross BlueShield \hfill \textit{Syracuse, NY}\\
Transformed team of existing solution architects to an enterprise focus to deliver key strategic artifacts. Applied business architecture/modeling to refining software design processes. Performed annual refreshes of strategies leading to actionable work plans aligned with corporate strategy. Frequent speaker and writer for both internal and external venues. Lead cross-divisional innovation efforts around product design and technology investments to improve customer intimacy.

Provided intellectual leadership around the discipline of Enterprise and Software Architecture using prominent techniques and collateral from the industry including the Zachman, TOGAF frameworks. Led roll-out of Enterprise Architecture modeling tool (MEGA) to improve documentation practices. 

Executed role of lead software architect and project manager for J2EE software projects including PHR and eRx applications with heavy integration requirements. Unified Java development efforts across enterprise by establishing and disseminating Java development standards via quarterly conferences.

\textbf{Adjunct Instructor, Internet \& J2EE} \hfill Sep 1996 - Dec 2010\\
Syracuse University \hfill \textit{Syracuse, NY}\\
\textbf{Managing Software Architect} \hfill Sep 1996 - May 2021\\
AppliedTheory \hfill \textit{Syracuse, NY}\\
\textbf{Managing Software Architect} \hfill Aug 1995 - Sep 1996\\
Questra Consulting \hfill \textit{Syracuse, NY}\\
\textbf{Ascending Software Development Roles} \hfill Dec 1987 - Aug 1995\\
Mutual of New York / CSC \hfill \textit{Syracuse, NY}\\

\begin{rSection}{Education}
{\bf Bachelor of Science \emph{summa cum laude}. Business Administration - MIS}, Syracuse University \hfill {May 1987}\\
\end{rSection}

\begin{rSection}{Certifications \& Accreditations}
\begin{itemize}
  \item Azure AI Fundamentals. March 2021.
  \item Google Cloud Certified - Professional Cloud Architect. April 2019.
  \item AWS Certified Developer Associate. October 2018.
  \item AWS Certified Solution Architect. September 2018.
  \item Oracle Business Architecture Certified. Oracle Corporation. December 2013.
  \item Oracle Enterprise Architecture Certified. Oracle Corporation. April 2012.
  \item TOGAF 9 Level 2 Certification. The Open Group. 2011.
  \item Sun Certified Enterprise Architect for J2EE. Sun Microsystems. ca. 2005.
  \item Sun Certified Java Programmer. Sun Microsystems. 2002.
\end{itemize}
\end{rSection}

\begin{rSection}{Awards}
  \begin{itemize}
   \itemsep -3pt {} 
   \item Commvault - Gold star award. FY2021Q2.
   \item Commvault - Wingman Award. FY2018Q4.
   \item Commvault - Above \& Beyond. FY2018Q1.
   \item OEA of the Year. Oracle Corporation. FY2013.
   \item OEA of the Quarter. Oracle Corporation. FY2011Q3.
   \item IT Professional of the Year. Excellus BlueCross BlueShield. 2005.
  \end{itemize}  
\end{rSection}

\end{document}